---
title: "Challenge-4"
author: "Ian Lee"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<style>
p.comment {
background-color: #DBDBDB;
padding: 10px;
border: 1px solid black;
margin-left: 25px;
border-radius: 5px;
font-style: italic;
}

</style>

## Questions
<br>

Load the "CommQuest2023.csv" dataset using the `read_csv()` command and assign it to a variable named "comm_data." 

```{r, eval=TRUE,echo=TRUE}
# Enter code here
library("tidyverse")
library("dplyr")
comm_data <- read_csv("CommQuest2023_Larger.csv")
```
<br>


#### Question-1: Communication Chronicles

Using the select command, create a new dataframe containing only the "date," "channel," and "message" columns from the "comm_data" dataset.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
selected_columns <- comm_data %>%
  select(date, channel, message)
print(selected_columns)
```
<br>

#### Question-2: Channel Selection

Use the filter command to create a new dataframe that includes messages sent through the "Twitter" channel on August 2nd.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
aug_2nd_twitter <- comm_data %>%
  filter(channel == "Twitter", date == "2023-08-02")
print(aug_2nd_twitter)
```
<br>

#### Question-3: Chronological Order

Utilizing the arrange command, arrange the "comm_data" dataframe in ascending order based on the "date" column.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
asc_data <- comm_data %>%
  arrange(date)
print(asc_data)
```
<br>

#### Question-4: Distinct Discovery

Apply the distinct command to find the unique senders in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
unique_senders <- comm_data %>%
  distinct(sender)
print(unique_senders)
```
<br>

#### Question-5: Sender Stats

Employ the count and group_by commands to generate a summary table that shows the count of messages sent by each sender in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
message_data <- comm_data %>%
  group_by(sender) %>%
  count()
print(message_data)
```
<br>

#### Question-6: Channel Chatter Insights

Using the group_by and count commands, create a summary table that displays the count of messages sent through each communication channel in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
channel_data <- comm_data %>%
  group_by(channel) %>%
  count()
print(channel_data)
```
<br>

#### Question-7: Positive Pioneers

Utilize the filter, select, and arrange commands to identify the top three senders with the highest average positive sentiment scores. Display their usernames and corresponding sentiment averages.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
top_senders <- comm_data %>%
  filter(sentiment > 0) %>%
  select(sender, sentiment) %>%
  group_by(sender) %>%
  summarize(average_sentiment = mean(sentiment)) %>%
  arrange(desc(average_sentiment)) %>%
  slice(1:3)
print(top_senders)
```
<br>

#### Question-8: Message Mood Over Time

With the group_by, summarise, and arrange commands, calculate the average sentiment score for each day in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
average_sentiment <- comm_data %>%
  group_by(date) %>%
  summarize(average_sentiment = mean(sentiment)) %>%
  arrange(date)
print(average_sentiment)
```
<br>

#### Question-9: Selective Sentiments

Use the filter and select commands to extract messages with a negative sentiment score (less than 0) and create a new dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
negative_messages <- comm_data %>%
  filter (sentiment < 0) %>%
  select(date, channel, sender, message, sentiment)
print(negative_messages)
```
<br>

#### Question-10: Enhancing Engagement

Apply the mutate command to add a new column to the "comm_data" dataframe, representing a sentiment label: "Positive," "Neutral," or "Negative," based on the sentiment score.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
sentiment_label <- comm_data %>%
  mutate(sentiment_label = ifelse(sentiment > 0, "Positive",
                                  ifelse(sentiment == 0, "Neutral", "Negative")))
print(sentiment_label)
```
<br>

#### Question-11: Message Impact

Create a new dataframe using the mutate and arrange commands that calculates the product of the sentiment score and the length of each message. Arrange the results in descending order.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
sentiment_product <- comm_data %>%
  mutate(product_sentiment_score_and_length = sentiment * nchar(message)) %>%
  arrange(desc(product_sentiment_score_and_length))
print(sentiment_product)
```
<br>

#### Question-12: Daily Message Challenge

Use the group_by, summarise, and arrange commands to find the day with the highest total number of characters sent across all messages in the "comm_data" dataframe.

**Solution:**

```{r, eval=TRUE,echo=TRUE}
# Enter code here
highest_characters <- comm_data %>%
  group_by(date) %>%
  summarise(character_count = sum(nchar(message))) %>%
  arrange(desc(character_count)) %>%
  head(1)
print(highest_characters)
```
<br>

#### Question-13: Untidy data

Can you list at least two reasons why the dataset illustrated in slide 10 is non-tidy? How can it be made Tidy?

**Solution:** Reason 1: It is untidy because there are multiple variables in columns. Reason 2: Under the column "percentage", there are numbers which do not fall under percentage. 